---
title: "R Resources"
description: |
  This page contains links to R resources & tutorials for each core topic covered in PAAS, AnD, DS & QQM
output:
  distill::distill_article:
    toc: true
    toc_float: true
    theme: dans-theme.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(xaringanExtra)
library(emo)
xaringanExtra::use_clipboard()
```

### Accessing Tutorials

Much of the R content is delivered through interactive tutorials. These tutorials need to be installed & run within RStudio. To install the packages required to run them ("learnr", "remotes", "paas", & "discovr"), type each of the commands in the code block below into the RStudio console one at a time and press Enter to run them.

Following installation, tutorials can be accessed through the "Tutorial" tab in RStudio, or by running the relevant code in the console.

```{r, eval = F, echo = T}

install.packages("learnr")
install.packages("remotes")
remotes::install_github("SussexPsychMethods/PAAS", build = FALSE, upgrade = "never")
remotes::install_github("profandyfield/discovr")

```

Most R skills are covered in several modules & in several tutorials/practicals. Where this repetition occurs, there are multiple resources to refer to for help!

<br>

### R, RStudio & General Computing

-   Installation of R & RStudio: [PAAS 00](https://canvas.sussex.ac.uk/courses/12684/pages/r-resources)

-   Tours of RStudio: [PAAS 01](https://paas.netlify.app/tut01_alternative/)

-   File paths:

```{r, eval = F, echo = T}
learnr::run_tutorial(name = "02_files_paths_projects", package = "paas")
```

-   R Projects: [PAAS 03](https://paas.netlify.app/practicals/02_project_files/slides/#1), [PAAS 08](https://paas.netlify.app/practicals/07_organizing_data/slides/#1)

-   R objects, functions & packages: [PAAS 05](https://paas.netlify.app/practicals/04_writing_code/worksheets/), [PAAS 06](https://paas.netlify.app/practicals/05_data_structures/slides/#1), [PAAS 07](https://paas.netlify.app/practicals/06_packages_functions/slides/#1), [PAAS 07](https://paas.netlify.app/practicals/06_packages_functions/worksheets/?type=tutor)

```{r, eval = F, echo = T}
learnr::run_tutorial(name = "04_basic_r", package = "paas")
```

```{r, eval = F, echo = T}
learnr::run_tutorial(name = "05_objects_functions_data", package = "paas")
```

```{r, eval = F, echo = T}
learnr::run_tutorial(name = "06_functions_packages", package = "paas")
```

```{r, eval = FALSE, echo = T}
learnr::run_tutorial(name = "discovr_01", package = "discovr")
```

<br>

### R Markdown

-   Basic R Markdown: [PAAS 04](https://paas.netlify.app/practicals/03_r_markdown/slides/#1)

```{r, eval = F, echo = T}
learnr::run_tutorial(name = "03_r_markdown", package = "paas")
```

-   Advanced R Markdown: [AnD 01](https://and.netlify.app/tutorials/01/)

<br>

### Importing & Organising Data

-   Import tidy data:

```{r, eval = F, echo = T}
learnr::run_tutorial(name = "07_organizing_data", package = "paas")
```

<br>

### Inspecting, Cleaning & Wrangling Data

-   Inspecting data: [AnD 03](https://and.netlify.app/practicals/03/worksheet/?sol=true#inspecting-data)

-   Wrangling data: [PAAS 09](https://paas.netlify.app/practicals/08_data_wrangling/slides/#1)

```{r, eval = FALSE, echo = T}
learnr::run_tutorial(name = "08_wrangling_data", package = "paas")
```

-   The pipe %\>% [PAAS 10](https://paas.netlify.app/practicals/09_grouping_summarising/slides/#1), [AnD 02](https://and.netlify.app/tutorials/02/)

```{r, eval = FALSE, echo = T}
learnr::run_tutorial(name = "09_summaries_and_pipes", package = "paas")
```

-   Data cleaning: [AnD 03](https://and.netlify.app/practicals/03/worksheet/?sol=true#cleaning), [AnD 04](https://and.netlify.app/practicals/04/worksheet/?sol=true#part-1-data-cleaning)

-   Creating composites: [AnD 07](https://and.netlify.app/tutorials/07/)

-   Checking dodgy data:

```{r, eval = FALSE, echo = T}
learnr::run_tutorial(name = "discovr_06", package = "discovr")
```

-   Centring variables:

```{r, eval = FALSE, echo = T}
learnr::run_tutorial(name = "discovr_10", package = "discovr")
```

<br>

### Summarising Data

-   Basic summary tables: [PAAS 10](https://paas.netlify.app/practicals/09_grouping_summarising/slides/#1), [AnD 03](https://and.netlify.app/practicals/03/worksheet/?sol=true#descriptives)

```{r, eval = FALSE, echo = T}
learnr::run_tutorial(name = "09_summaries_and_pipes", package = "paas")
```

-   Pretty tables: [PAAS 11](https://paas.netlify.app/practicals/10_tables_and_plots/slides/#1)

-   Plots: [PAAS 11](https://paas.netlify.app/practicals/10_tables_and_plots/slides/#1), [AnD](https://and.netlify.app/practicals/02/worksheet/?sol=true#part-2-tables-and-visualisations)

```{r, eval = FALSE, echo = T}
learnr::run_tutorial(name = "discovr_05", package = "discovr")
```

-   Summary stats & CIs:

```{r, eval = FALSE, echo = T}
learnr::run_tutorial(name = "discovr_02", package = "discovr")
```

```{r, eval = FALSE, echo = T}
learnr::run_tutorial(name = "discovr_03", package = "discovr")
```

<br>

### Statistical Analyses

-   Correlation: [AnD 05](https://and.netlify.app/tutorials/05/)

```{r, eval = FALSE, echo = T}
learnr::run_tutorial(name = "discovr_07", package = "discovr")
```

-   Chi-Square: [AnD 06](https://and.netlify.app/tutorials/06/)

-   t-test: [AnD 07](https://and.netlify.app/tutorials/07/)

```{r, eval = FALSE, echo = T}
learnr::run_tutorial(name = "discovr_09", package = "discovr")
```

-   Linear model: [AnD 08](https://and.netlify.app/tutorials/08/), [AnD 09](https://and.netlify.app/tutorials/09/), [AnD 10](https://and.netlify.app/tutorials/10/), [AnD 11](https://and.netlify.app/tutorials/11/)

```{r, eval = FALSE, echo = T}
learnr::run_tutorial(name = "discovr_08", package = "discovr")
```

```{r, eval = FALSE, echo = T}
learnr::run_tutorial(name = "discovr_11", package = "discovr")
```

```{r, eval = FALSE, echo = T}
learnr::run_tutorial(name = "discovr_12", package = "discovr")
```

```{r, eval = FALSE, echo = T}
learnr::run_tutorial(name = "discovr_13", package = "discovr")
```

```{r, eval = FALSE, echo = T}
learnr::run_tutorial(name = "discovr_14", package = "discovr")
```

```{r, eval = FALSE, echo = T}
learnr::run_tutorial(name = "discovr_15", package = "discovr")
```

-   Moderation & mediation:

```{r, eval = FALSE, echo = T}
learnr::run_tutorial(name = "discovr_10", package = "discovr")
```

-   Exploratory factor analysis:

```{r, eval = FALSE, echo = T}
learnr::run_tutorial(name = "discovr_18", package = "discovr")
```

<br>

### Reporting Results

-   Inline code: [AnD 05](https://and.netlify.app/tutorials/05/#optional-inline-coding)

<br>
