---
title: "How Do I?"
description: |
  This page contains common questions & some answers! More coming soon!
output:
  distill::distill_article:
    toc: true
    toc_float: true
    theme: dans-theme.css

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(xaringanExtra)
xaringanExtra::use_clipboard()
library(emo)
```

### How Do I? `r emo::ji("thought_balloon")`

Change the parts in CAPS to match your data!

<details>
  <summary>How do I create a composite (mean) score?</summary>
<br>

```{r, eval = F, echo = T}
DATA <- DATA %>% 
    dplyr::rowwise() %>% 
    dplyr::mutate(
    NEW_COLUMN_NAME = mean(c(VARIABLE1, VARIABLE2, VARIABLE3)))
```



*Any rows with missing data will have NA in the new column*

</details>

<details>
  <summary>How do I create a composite (mean) score when I have missing data?</summary>

<br>

```{r, eval = F, echo = T}
DATA <- DATA %>% 
    dplyr::rowwise() %>% 
    dplyr::mutate(
    NEW_COLUMN_NAME = mean(c(VARIABLE1, VARIABLE2, VARIABLE3), na.rm = TRUE))
```

*By including the na.rm argument, we can calculate the mean of our variables, even where there is missing data in any of them*

</details>



<details>
  <summary>How do I create a composite (mean) score with a certain amount of missing data?</summary>



```{r, eval = F, echo = T}
VARIABLE_MEAN <- DATA %>% 
      dplyr::select(VARIABLE1, VARIABLE2, VARIABLE3) %>% 
      sjstats::mean_n(., 2) %>% 
      tibble::as_tibble_col(., column_name = "VARIABLE_MEAN")

DATA <- cbind(DATA, VARIABLE_MEAN)
```


*The first part creates a mean of the variables we have selected, only where there are at least 2 responses (you can use any number here in the mean_n() function), and produces a tibble called varible_mean which contains those values. The second part binds that new column to our existing data*


</details>


<br>

#### Submit your 'How do I?' [here](https://docs.google.com/forms/d/e/1FAIpQLScNFE9GSstJNGIe_RsKRO5LoUgzv4st-Pzu610Sz-pdiyRBtA/viewform?usp=sf_link)


<iframe src="https://docs.google.com/forms/d/e/1FAIpQLScNFE9GSstJNGIe_RsKRO5LoUgzv4st-Pzu610Sz-pdiyRBtA/viewform?embedded=true" width="640" height="510" frameborder="0" marginheight="0" marginwidth="0">Loading…</iframe>

<br>

