---
title: "Week 05: Data Wrangling"
output:
  distill::distill_article:
    toc: true
    toc_float: true
    theme: dans-theme.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
xaringanExtra::use_clipboard()
```

### HappyHouR 

Slides [(*open in a new tab*)](https://fundrmentals-slides.netlify.app/week_05/index.html){target="_blank"}

<!--

<iframe id="inlineFrameExample"
    title="Inline Frame Example"
    height="360"
    src="./week_04/index.html">
</iframe>

-->

Download the [worksheet here](./docs/week_04.Rmd)


### Complete the tutorial for next week if you haven't already: 

:::ojtask

Work through the discovr_05 tutorial by pasting the below code into the **Console** in RStudio & pressing **Enter**.

```{r, eval = F, echo = T}

learnr::run_tutorial("discovr_05", package = "discovr")

```

:::

*This tutorial is pretty long, and generally visualising data isn't something we learn by heart (or need to), but you should aim to try go through the ggplot2 section as a minimum, then ideally complete the boxplots, plotting means, and scatterplots sections (you can ignore the faceting tasks if you want to). There's also an empty code chunk for you to have a go at creating a plot from the emp_data in the worksheet for week 04.*

<br>

<div class="button-box col-lg-12">

<a href="https://fundrmentals.netlify.app/week_04.html">
<button class="button3">Previous week</button>
</a>
<a href="https://fundrmentals.netlify.app/week_06.html">
<button class="button4">Next week</button>
</a>

</div>

<br>


<!-- :::ojtask -->

<!-- Work through the discovr_07 (associations) & the discovr_09 (comparing means) tutorials by pasting the below code into the **Console** in RStudio & pressing **Enter**. -->

<!-- ```{r, eval = F, echo = T} -->

<!-- learnr::run_tutorial("discovr_07", package = "discovr") -->

<!-- ``` -->

<!-- ```{r, eval = F, echo = T} -->

<!-- learnr::run_tutorial("discovr_09", package = "discovr") -->

<!-- ``` -->

<!-- ::: -->

<!-- <br> -->