---
title: "Week 03"
output:
  distill::distill_article:
    toc: true
    toc_float: true
    theme: dans-theme.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
xaringanExtra::use_clipboard()
```

### HappyHouR 

Slides [(*open in a new tab*)](){target="_blank"}

<iframe id="inlineFrameExample"
    title="Inline Frame Example"
    height="360"
    src="">
</iframe>


### Materials

Download the data file [here](https://raw.githubusercontent.com/de84sussex/sussex_fundrmentals/master/docs/empathy_data.csv), by right-clicking on the page that opens, and saving the file into the **data** folder of your fundRmentals R Project. 

The [dataset](https://journals.sagepub.com/doi/10.1177/0301006618809919) we're using examined whether people people differ on their empathy towards avatars when they are human-like vs robotic. 

There are four measures relating to the experimental design: **Participant ID**, **Condition** (1-4), **Humanness** (1 = Human-like, 2 = Robot-like), & **Harm** (1 = Unharmed, 2 = Harmed).

There are two participant demographic variables: **Gender** (1 = M, 2 = F) & **Age** (in years).

There are four outcome variables where participants were asked to rate whether the avatar can feel pain (variable name: **Pain**, scored from 1-7), whether it has experience (variable name: **Experience**, scored from 1-7), their level of empathy towards the avatar (variable name: **Q14097**, scored from 1-7), & their perceived attractiveness of the avatar (variable name: **Q15620**, scored from 1-7).


### Complete the tutorials for next week: 

:::ojtask

Work through the discovr_02 & the discovr_05 tutorials by pasting the below code into the **Console** in RStudio & pressing **Enter**.

```{r, eval = F, echo = T}

learnr::run_tutorial("discovr_02", package = "discovr")

```

```{r, eval = F, echo = T}

learnr::run_tutorial("discovr_05", package = "discovr")

```

:::

<br>
