---
title: "Week 10: ANOVA"
output:
  distill::distill_article:
    toc: true
    toc_float: true
    theme: dans-theme.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
xaringanExtra::use_clipboard()
```

### HappyHouR 

Slides [(*open in a new tab*)](https://fundrmentals-slides.netlify.app/week_10/index.html){target="_blank"}

<!--

<iframe id="inlineFrameExample"
    title="Inline Frame Example"
    height="360"
    src="">
</iframe>
-->

### Complete the tutorial for next week based on the test you use most often: 

:::ojtask

Work through either the discovr_10 (moderation & mediation), discovr_12 (ANCOVA), discovr_13 (factorial designs), discovr_14 (repeated measures designs), discovr_15 (mixed designs), discovr_17 (exploratory factor analysis), or discovr_20 (logistic regression) tutorial by pasting the below code into the **Console** in RStudio & pressing **Enter**.

```{r, eval = F, echo = T}
learnr::run_tutorial("discovr_10", package = "discovr")
```

```{r, eval = F, echo = T}
learnr::run_tutorial("discovr_12", package = "discovr")
```

```{r, eval = F, echo = T}
learnr::run_tutorial("discovr_13", package = "discovr")
```

```{r, eval = F, echo = T}
learnr::run_tutorial("discovr_14", package = "discovr")
```

```{r, eval = F, echo = T}
learnr::run_tutorial("discovr_15", package = "discovr")
```

```{r, eval = F, echo = T}
learnr::run_tutorial("discovr_17", package = "discovr")
```

```{r, eval = F, echo = T}
learnr::run_tutorial("discovr_20", package = "discovr")
```

:::

<br>
