---
title: "Week 02: R Basics"
output:
  distill::distill_article:
    toc: true
    toc_float: true
    theme: dans-theme.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
xaringanExtra::use_clipboard()
library(emo)
```


### HappyHouR 

Slides [(*open in a new tab*)](https://fundrmentals-slides.netlify.app/week_02/index.html){target="_blank"}


<!--

<iframe id="inlineFrameExample"
    title="Inline Frame Example"
    height="360"
    src="https://fundrmentals.netlify.app/week_02/index.html">
</iframe>
-->

### Materials

Download the data file [here](https://raw.githubusercontent.com/de84sussex/sussex_fundrmentals/master/docs/empathy_data.csv), by right-clicking on the page that opens, and saving the file into the **data** folder of your R Project. 


### Complete the tutorial for next week: 

You need to install the `discovr` package to complete this week's tutorial.

If you didn't install it in the HappyHouR this week, open RStudio, paste each line of code below into the **Console**, & press **Enter** to run them one by one. 

```{r, eval = F, echo = T}
install.packages("learnr")
```

```{r, eval = F, echo = T}
install.packages("remotes")
```

```{r, eval = F, echo = T}
remotes::install_github("profandyfield/discovr")
```

Once installed, you can access the tutorial for this week using the code below.

:::ojtask

Work through the discovr_01 tutorial by pasting the below code into the **Console** in RStudio & pressing **Enter**.

```{r, eval = F, echo = T}

learnr::run_tutorial("discovr_01", package = "discovr")

```

:::

*See how the tutorials work in [this video..](https://www.youtube.com/watch?v=FhoYCsZttGc){target="_blank"}*

<br>

<div class="button-box col-lg-12">

<a href="https://fundrmentals.netlify.app/week_01.html">
<button class="button3">Previous week</button>
</a>
<a href="https://fundrmentals.netlify.app/week_03.html">
<button class="button4">Next week</button>
</a>

</div>

<br>


