---
title: "Week 02"
output:
  distill::distill_article:
    toc: true
    toc_float: true
    theme: dans-theme.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
xaringanExtra::use_clipboard()
```


### HappyHouR 

Slides [(*open in a new tab*)](){target="_blank"}

<iframe id="inlineFrameExample"
    title="Inline Frame Example"
    height="360"
    src="">
</iframe>


### Complete the tutorial for next week: 

You need to install the `discovr` package to complete this week's tutorial.

If you didn't install it in the HappyHouR last week, open RStudio, paste each line of code below into the **Console**, & press **Enter** to run them one by one. 

```{r, eval = F, echo = T}

install.packages("learnr")
install.packages("remotes")
remotes::install_github("profandyfield/discovr")

```


:::ojtask

Work through the discovr_01 tutorial by pasting the below code into the **Console** in RStudio & pressing **Enter**.

```{r, eval = F, echo = T}

learnr::run_tutorial("discovr_01", package = "discovr")

```

:::

<br>

